Blockchain as Middleware Services for\\Transactive Energy Applications

### 2017-05-01 notes/initial_writeup/paper.tex
no message

@@

\begin{figure*}
\begin{tikzpicture}[
  x=1cm, 
  y=1cm,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm}]

@@

\foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
  \node [regular polygon, regular polygon sides=5, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{tAnchorRight/2.5/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
\end{scope}

@@

\foreach \name/\x/\y in {{pAnchorLeft/-0.6/0.7}, {pAnchorRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};

\end{scope}

@@

\foreach \name/\x/\y in {{mAnchorRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=0.4cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};

\end{scope}

@@

\foreach \name/\x/\y in {{lAnchorLeft/-0.5/0.7}, {lAnchorTopLeft/0/1.6}, {lAnchorTopRight/1.6/1.0}}
  \coordinate (\name) at (\x,\y);

@@

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};

\end{scope}

% additional nodes

\node [ellipse, nodeStyle] (dso) at (15.5cm, 3.0cm) {DSO node};

\draw [->, very thick, >=stealth, bend right=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, above left=0.0cm, align=center] {regulatory\\[-0.25em]transactions} (lAnchorTopRight);
\draw [<-, very thick, >=stealth, bend left=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, below right=0.0cm, align=center] {ledger status} (lAnchorTopRight);

% connections between systems
\draw [<-, very thick, >=stealth, bend left=5] ([yshift=0.0cm]tAnchorRight) to node [midway, above=0.1cm] {bids} ([yshift=0.0cm]pAnchorLeft);
\draw [->, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]tAnchorRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pAnchorLeft);

\draw [->, very thick, >=stealth, bend left=5] ([yshift=0.0cm]pAnchorRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0.0cm]lAnchorLeft);
\draw [<-, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]pAnchorRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lAnchorLeft);

\draw [->, very thick, >=stealth, bend left=15] ([yshift=0.2cm]mAnchorRight) to node [midway, above right=0.0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lAnchorTopLeft);
\draw [<-, very thick, >=stealth, bend right=-5] ([yshift=-0.2cm]mAnchorRight) to node [midway, below left=0.0cm] {ledger status} ([yshift=-0.2cm]lAnchorTopLeft);

@@

\begin{algorithm}[h!]
\caption{Validation of Financial Transaction}
\label{alg:validateFinancialTransaction}
\begin{algorithmic}[1]
\State{let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively}
\State{$NetBuy \gets 0$}
\For{valid transaction on the ledger}
  \If{time step is $T$ and buyer is $p_b$}
    \State{$NetBuy \gets NetBuy + $ energy amount}
  \EndIf
  \If{time step is $T$ and seller is $p_b$}
    \State{$NetBuy \gets NetBuy - $ energy amount}
  \EndIf
\EndFor
\State{$NetSell \gets 0$}
\For{valid transaction on the ledger}
  \If{time step is $T$ and seller is $p_b$}
    \State{$NetSell \gets NetSell + $ energy amount}
  \EndIf
  \If{time step is $T$ and buyer is $p_b$}
    \State{$NetSell \gets NetSell - $ energy amount}
  \EndIf
\EndFor
\If{$NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future}
  \State{\textbf{return} valid}
\Else
  \State{\textbf{return} invalid}
\EndIf
%
%\State{$A \gets (\emptyset, \emptyset)$} 
%\State{$\Loss^* \gets -\infty$}
%\For{$b = 1, \ldots, B_A$}
%  \For{$v \in V_A$}
%    \For{$k \in \Gamma^{-1}(v)$}
%      \State{$A' \gets A \cup \left(\{s\}, \left\{\hat{p}_{kv} = 1, \forall j \neq k : \hat{p}_{jv} = 0\right\}\right)$}
%      \State{$\Loss' \gets \big[\left(1 - \Pr[\text{detect}]\right) \cdot \Loss(C, A)$}
%      \State{\hspace{3.5em} $+ \Pr[\text{detect}] \cdot \min_M \max_R \Loss(C, A, M, R) \big]$}
%      \If{$\Loss' \geq \Loss^*$}
%        \State{$A^* \gets A'$}
%        \State{$\Loss^* \gets \Loss'$}
%      \EndIf
%    \EndFor
%    \State{$A \gets A^*$}
%  \EndFor
%\EndFor
%\State{Output $A$}
\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Timing}

\todo[inline]{
\textbullet 
look up timing assumptions from proposal, which are driven by control requirements
\textbullet 
map those timing assumptions to time interval in the transactive microgrid system
\textbullet 
discuss how supply and demand can be forecasted from energy trading between prosumers
}

@@

\begin{figure*}[h!]
\begin{tikzpicture}[
  x=1cm, 
  y=1cm,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
  linkStyle/.style={<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
  batchStyle/.style={->, very thick, >=stealth},
  braceStyle/.style={decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm},
]

@@

\foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
  \node [nodeStyle, regular polygon, regular polygon sides=5] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{tRight/2.5/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
  \draw [linkStyle] (\from) -- (\to);

\draw [braceStyle] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
\end{scope}

@@

\foreach \name/\x/\y in {{pLeft/-0.6/0.7}, {pRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
  \draw [linkStyle, dashed] (\from) -- (\to);

\draw [braceStyle] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};
\end{scope}

@@

\foreach \name/\x/\y in {{mRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
  \draw [linkStyle, dashed] (\from) -- (\to);

\draw [braceStyle, yshift=0.8cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};
\end{scope}

@@

\foreach \name/\x/\y in {{lLeft/-0.5/0.7}, {lTopLeft/0/1.6}, {lTopRight/1.6/1.0}}
  \coordinate (\name) at (\x,\y);

@@

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};
\end{scope}

% additional nodes
\node [ellipse, nodeStyle] (dso) at (15cm, 3.1cm) {DSO node};

\draw [->, >=stealth, bend right=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, above left=0cm, align=center] {regulatory\\[-0.25em]transactions} (lTopRight);
\draw [<-, >=stealth, bend left=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, below right=0cm, align=center] {ledger status} (lTopRight);

\node [above=1.2cm of dso] (controller) {control algorithm};

\draw [<-, >=stealth, bend right=10, shorten <=1.5pt] (dso) to node [midway, left=0.3cm, align=center] {measured and\\[-0.25em]expected load} (controller);
\draw [->, >=stealth, bend left=10, shorten <=1.5pt] (dso) to node [midway, right=0.3cm, align=center] {control\\[-0.25em]signal} (controller);

% connections between systems
\draw [batchStyle, <-, bend left=5] (tRight) to node [midway, above=0.1cm] {bids} (pLeft);
\draw [batchStyle, bend right=5] ([yshift=-0.4cm]tRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pLeft);

\draw [batchStyle, bend left=5] (pRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0cm]lLeft);
\draw [batchStyle, <-, bend right=5] ([yshift=-0.4cm]pRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lLeft);

\draw [batchStyle, bend left=15] ([yshift=0.2cm]mRight) to node [midway, above right=0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lTopLeft);
\draw [batchStyle, <-, bend right=-5] ([yshift=-0.2cm]mRight) to node [midway, below left=0cm] {ledger status} ([yshift=-0.2cm]lTopLeft);

@@

\begin{algorithm}[h!]
\caption{Validation of Financial Transaction}
\label{alg:validateFinancialTransaction}
\begin{algorithmic}[1]
\Statex{\hspace{-\algorithmicindent}\textbf{Input:} incoming transaction, valid transactions on the ledger}
\Statex{\hspace{-\algorithmicindent}\textbf{Output:} valid / invalid}
\State{let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively}
\State{$NetBuy \gets 0$}
\State{$NetSell \gets 0$}
\For{valid transaction on the ledger}
  \If{time step is $T$}
    \If{buyer is $p_b$}
      \State{$NetBuy \gets NetBuy + $ energy amount}
    \EndIf
    \If{seller is $p_b$}
      \State{$NetBuy \gets NetBuy - $ energy amount}
    \EndIf
    \If{seller is $p_s$}
      \State{$NetSell \gets NetSell + $ energy amount}
    \EndIf
    \If{buyer is $p_s$}
      \State{$NetSell \gets NetSell - $ energy amount}
    \EndIf
  \EndIf
\EndFor
\If{$NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future}
  \State{\textbf{return} valid}
\Else
  \State{\textbf{return} invalid}
\EndIf
%
%\State{$A \gets (\emptyset, \emptyset)$} 
%\State{$\Loss^* \gets -\infty$}
%\For{$b = 1, \ldots, B_A$}
%  \For{$v \in V_A$}
%    \For{$k \in \Gamma^{-1}(v)$}
%      \State{$A' \gets A \cup \left(\{s\}, \left\{\hat{p}_{kv} = 1, \forall j \neq k : \hat{p}_{jv} = 0\right\}\right)$}
%      \State{$\Loss' \gets \big[\left(1 - \Pr[\text{detect}]\right) \cdot \Loss(C, A)$}
%      \State{\hspace{3.5em} $+ \Pr[\text{detect}] \cdot \min_M \max_R \Loss(C, A, M, R) \big]$}
%      \If{$\Loss' \geq \Loss^*$}
%        \State{$A^* \gets A'$}
%        \State{$\Loss^* \gets \Loss'$}
%      \EndIf
%    \EndFor
%    \State{$A \gets A^*$}
%  \EndFor
%\EndFor
%\State{Output $A$}
\end{algorithmic}
\end{algorithm}
